---
title: "Age & Wage"
output:
  rmdformats::html_docco:
    highlight: kate
    date: "2022-09-22"
runtime: shiny
---

```{r setup,  include = FALSE }
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(ggplot2)
Data <- read.csv(choose.files())
```

<h1 style="font-size:25px;">Summary</h1>
We will describe the distribution of age and wage with histograms. The distributions can be changed by changing the number of bins (depending on the ranges of the values).
The user is allowed to switch between the two variables and play with the number of bins, and also he will see the descriptive statistics of each variable.

We also sought the link between age and wage, by building a quadratic (second-order) polynomial model.

The application allows to predict the income of the person by inserting the age.


```{r eruptions, echo=TRUE}

ui <- fluidPage(
  titlePanel("Age and Wage"),
  sidebarLayout(
    sidebarPanel(
      selectInput("Choosevariable", "Choise of variable",
                  choices = c("wages", "ages"),
                  selected = "wages"),
      sliderInput("bins",
                  "Number of bins:",
                  min = 10,
                  max = 50,
                  value = 30),
      sliderInput("age",
                  "Insert your age for wage prediction:",
                  min =18,
                  max = 80,
                  value=25)
    ),
    mainPanel(
      tableOutput("reg"),
      plotOutput("distPlot"),
      textOutput("label"),
      verbatimTextOutput("summary"),
      plotOutput("plot", click = "plot_click"),
      verbatimTextOutput("info"))
    )
  )

```


```{r}

server <- function(input, output) {
  output$reg <- renderTable({
    poly_reg <- lm(wage ~ poly(age, 2, raw = TRUE),
                   data = Data)
    NewAge <- data.frame(age=input$age)
    InsiertValue <- predict(object = poly_reg,newdata = NewAge)
    InsiertValue}
  )
  output$info <- renderText({
    paste("Age=", input$plot_click$x, "\nWage=", input$plot_click$y )
  })
  output$distPlot <- renderPlot({
    if (input$Choosevariable == "wages") {x    <- Data[, 11]}
    if (input$Choosevariable == "ages") {x    <- Data[, 2]}
    bins <- seq(min(x), max(x), length.out = input$bins + 1)
    
    hist(x, breaks = bins, col = '#FFDB6D', border = 'black',
         xlab = input$Choosevariable,
         main = paste("Histogram of", input$Choosevariable) )
  })
  
    

  output$summary <- renderPrint({
    if (input$Choosevariable == "wages") {x<- Data[, 11]}
    if (input$Choosevariable == "ages") {x<- Data[, 2]}
    summary(x)
  })

   output$label <- renderText({
     paste("Summary of", input$Choosevariable)
   })
  
  output$plot<- renderPlot({
    x <- Data$age
    y <- Data$wage
    ggplot(Data,aes(x=age,y=wage))+
      geom_point()+ggtitle("Plot: Age & Wage, and Model line (poly 2 degree)")+
      geom_smooth(method = "lm", formula = y ~ poly(x, 2), size = 1, colour= "blue")+
      scale_x_continuous(name="Age")+
      scale_y_continuous(name="Wage")+
      theme(plot.title=element_text(hjust=0.5,size = 15, face = "bold"),
            panel.background = element_rect(fill = "linen", colour = "grey50"),
            axis.title.y.left = element_text(hjust = 0.5, colour = ,size = 10, face = "bold") ,
            axis.title.x =element_text(hjust =0.5 ,colour = ,size = 10, face = "bold") ,
            axis.text.x = element_text(colour = "black")
            
      )}
  )

}
```

<h1 style="font-size:25px;">Application</h1>
```{r, echo=FALSE}
shinyApp(ui = ui, server = server)

```



