---
title: "Age & Wage"
output:
  rmdformats::html_docco:
    highlight: kate
    date: "2022-09-22"
runtime: shiny
---

```{r setup,  include = FALSE }
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(ggplot2)
library(caret)
Data <- read.csv(choose.files())
```

<h1 style="font-size:25px;">Summary</h1>
Our data includes 3000 observations of two variables: 
<br /> 1. Wage - yearly income in thousands dollars.
<br />2. Age

The following application will be used to describe the distribution of age and wage with histograms. The distributions can be changed by changing the number of bins (meaning more bins, will cause smaller range of values in each bin). The user is allowed to switch between the two variables and play with the number of bins, while choosing each of the variables he will see the corresponded descriptive statistics.

In addition, We sought the link between age and wage by fitting to it two models:
<br />1. a linear model
<br />2. a quadratic model
<br />When age was the predictor and wage was the predicted.

The application shows, each RMSE under each model plot. we have found that the better fitted model is the quadratic model (smaller RMSE). This means that the link between age and wage is not linear, meaning income does not increases with age. But when people are young or old their income is relatively low, while in the middle ages people has the highest income.

The user has also an option to click on the quadratic model plot, and see the values (age and wage) of a specific observation.

Finally, the application allows to predict the income by inserting an age value. The prediction is done with the quadratic model since it's the better model.




```{r eruptions, echo=FALSE}

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      selectInput("Choosevariable", "Choise of variable",
                  choices = c("wages", "ages"),
                  selected = "wages"),
      sliderInput("bins",
                  "Number of bins:",
                  min = 10,
                  max = 50,
                  value = 30),
      sliderInput("age",
                  "Insert your age for wage prediction (poly model):",
                  min =18,
                  max = 80,
                  value=25)
    ),
    mainPanel(
      tableOutput("reg"),
      plotOutput("distPlot"),
      textOutput("label"),
      verbatimTextOutput("summary"),
      plotOutput("plotLinear"),
      textOutput("labelRMSE1"),
      verbatimTextOutput("RMSE1"),
      plotOutput("plotQuadric", click = "plot_click"),
      textOutput("labelRMSE2"),
      verbatimTextOutput("RMSE2"),
      verbatimTextOutput("info")
    )
  )
)
```


```{r, echo=FALSE}

server <- function(input, output) {
  output$reg <- renderTable({
    poly_reg <- lm(wage ~ poly(age, 2, raw = TRUE),
                   data = Data)
    NewAge <- data.frame(age=input$age)
    InsiertValue <- predict(object = poly_reg,newdata = NewAge)
    InsiertValue}
  )
  output$info <- renderText({
    paste("Age=", input$plot_click$x, "\nWage=", input$plot_click$y)
  }
  )
  
  output$distPlot <- renderPlot({
    if (input$Choosevariable == "wages") {x    <- Data[, 2]}
    if (input$Choosevariable == "ages") {x    <- Data[, 1]}
    bins <- seq(min(x), max(x), length.out = input$bins + 1)
    
    hist(x, breaks = bins, col = '#FFDB6D', border = 'black',
         xlab = input$Choosevariable,
         main = paste("Histogram of", input$Choosevariable) )
  })
  
    

  output$summary <- renderPrint({
    if (input$Choosevariable == "wages") {x<- Data[, 2]}
    if (input$Choosevariable == "ages") {x<- Data[, 1]}
    summary(x)
  })
   output$RMSE1 <- renderPrint({
     linear <- lm(wage ~ age, data = Data)
     predictLinear <- predict(linear, Data)
     cat(RMSE(predictLinear, Data$wage))
  })
   

    output$RMSE2 <- renderPrint({
      poly <- lm(wage ~ poly(age, 2, raw = TRUE), data = Data) 
    predictPoly <- predict(poly, Data)
     cat(RMSE(predictPoly, Data$wage))
  }) 

   output$label <- renderText({
     paste("Summary of", input$Choosevariable)
   })
    output$labelRMSE1 <- renderText({
     paste("RMSE of linear model:")
   })
    output$labelRMSE2 <- renderText({
     paste("RMSE of quadric model:")
   })
    output$plotLinear<- renderPlot({
    x <- Data$age
    y <- Data$wage
    ggplot(Data,aes(x=age,y=wage))+
      geom_point()+ggtitle("Plot 1, Linear Model")+
      geom_smooth(method = "lm", formula = y ~ x, size = 1, colour= "blue")+
      scale_x_continuous(name="Age")+
      scale_y_continuous(name="Wage")+
      theme(plot.title=element_text(hjust=0.5,size = 15, face = "bold"),
            panel.background = element_rect(fill = "linen", colour = "grey50"),
            axis.title.y.left = element_text(hjust = 0.5, colour = ,size = 10, face = "bold") ,
            axis.title.x =element_text(hjust =0.5 ,colour = ,size = 10, face = "bold"),
            axis.text.x = element_text(colour = "black")
            
      )}
    )
  
  output$plotQuadric<- renderPlot({
    x <- Data$age
    y <- Data$wage
    ggplot(Data,aes(x=age,y=wage))+
      geom_point()+ggtitle("Plot 2, Quadric Model")+
      geom_smooth(method = "lm", formula = y ~ poly(x, 2), size = 1, colour= "blue")+
      scale_x_continuous(name="Age")+
      scale_y_continuous(name="Wage")+
      theme(plot.title=element_text(hjust=0.5,size = 15, face = "bold"),
            panel.background = element_rect(fill = "linen", colour = "grey50"),
            axis.title.y.left = element_text(hjust = 0.5, colour = ,size = 10, face = "bold") ,
            axis.title.x =element_text(hjust =0.5 ,colour = ,size = 10, face = "bold") ,
            axis.text.x = element_text(colour = "black")
            
      )}
  )

}
```

<h1 style="font-size:25px;">Application</h1>
```{r, echo=FALSE}
shinyApp(ui = ui, server = server)

```



